Decoupled wood and leaf strategies among canopy and understorey tree in a low-elevation rainforest of India

### 2018-11-13 draft.Rmd
Uppangala 0.1.9052 Plot map

```{r Uppangala, fig.cap="Canopy model of the 10-ha forest permanent plot in Uppangala, India. Preliminry figure to be improved."}
knitr::include_graphics("./data/Plot.png")
```

@@

```{r GWMboxplot, fig.cap="Boxplot of guilds weighted means (GWM) among communties for each traits (for canopy (C) and understorey (U) guilds). See table \\@ref(tab:Traits) for abbreviations.", fig.height=4}
L %>%
  melt(id.var = "com",
       variable.name = "SpCode",
       value.name = "abundance") %>% 
  dcast(SpCode ~ com, value.var = "abundance") %>% 
  mutate(SpCode = as.character(SpCode)) %>% 
  inner_join(Q, by = "SpCode") %>%
  select(-SpCode) %>%
  melt(id.vars = c('strata', 'LES', 'SLA', 'WES', 'WD', 'LDMC', 'LA', 'LT'),
       variable.name = 'community', value.name = 'abundance') %>%
  group_by(strata, community) %>%
  summarise_each(funs(weighted.mean(., abundance, na.rm = T)), -abundance) %>% 
  select(-community, -LES, -WES) %>% 
  melt(id.vars = "strata", 
       variable.name = "trait",
       value.name = "GWM") %>% 
  ggplot(aes(x = strata, y = GWM, fill = strata)) +
  geom_boxplot() +
  facet_wrap(~trait, scales = "free", nrow = 1) +
  xlab("Guild") + scale_fill_discrete(guide = "none") +
  ggpubr::stat_compare_means(aes(label = paste(..p.signif..))) 
```

>>>>

```{r Uppangala, fig.cap="Canopy model of the 10-ha forest permanent plot in Uppangala, India. Preliminry figure to be improved."}
DCM <- raster("./data/Canopy.tif")
crs(DCM) <- '+proj=utm +zone=43 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0'
DEM <- raster("./data/DEM.tif")
crs(DEM) <- '+proj=utm +zone=43 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0'
limits <- shapefile("./data/Plots/Shapeall10ha.shp")
DCM <- crop(DCM, limits)
DEM <- crop(DEM, limits)
DEM_spdf <- as(DEM, "SpatialPixelsDataFrame")
DEM_df <- as.data.frame(DEM_spdf)
colnames(DEM_df) <- c("Elevation", "x", "y")
DEM_plot <- ggplot() +  
  geom_tile(data=DEM_df, aes(x=x, y=y, fill=Elevation), alpha=0.8) + 
  scale_fill_distiller(palette = "Spectral") +
  coord_equal() +
  cowplot::theme_map()
DCM_spdf <- as(DCM, "SpatialPixelsDataFrame")
DCM_df <- as.data.frame(DCM_spdf)
colnames(DCM_df) <- c("Height", "x", "y")
DCM_plot <- ggplot() +  
  geom_tile(data=DCM_df, aes(x=x, y=y, fill=Height), alpha=0.8) + 
  coord_equal() +
  cowplot::theme_map() +
  scale_fill_distiller(palette = "Spectral")
ggsave(cowplot::plot_grid(DEM_plot, DCM_plot, labels = c("a) Elevation (m)", "b) Canopy height (m)")), 
       file = "Plot.png",
       path = './data/',
       width = 200, height = 100, unit = 'mm',
       dpi = 300)
```

@@

```{r GWMboxplot, fig.cap="Boxplot of guilds weighted means (GWM) among communties for each traits (for canopy (C) and understorey (U) guilds). See table \\@ref(tab:Traits) for abbreviations.", fig.height=4}
L %>%
  melt(id.var = "com",
       variable.name = "SpCode",
       value.name = "abundance") %>% 
  dcast(SpCode ~ com, value.var = "abundance") %>% 
  mutate(SpCode = as.character(SpCode)) %>% 
  inner_join(Q, by = "SpCode") %>%
  select(-SpCode) %>%
  melt(id.vars = c('strata', 'LES', 'SLA', 'WES', 'WD', 'LDMC', 'LA', 'LT'),
       variable.name = 'community', value.name = 'abundance') %>%
  group_by(strata, community) %>%
  summarise_each(funs(weighted.mean(., abundance, na.rm = T)), -abundance) %>% 
  # select(-community, -LES, -WES) %>% 
  # select(-community, -SLA, -WD, -LDMC, -LA, -LT) %>% 
  select(-community) %>% 
  melt(id.vars = "strata", 
       variable.name = "trait",
       value.name = "GWM") %>% 
  ggplot(aes(x = strata, y = GWM, fill = strata)) +
  geom_boxplot() +
  # facet_wrap(~trait, scales = "free", nrow = 1) +
  facet_wrap(~trait, scales = "free", nrow = 2) +
  xlab("Guild") + scale_fill_discrete(guide = "none") +
  ggpubr::stat_compare_means(aes(label = paste(..p.signif..))) 
```
